---
title: "Homework 1"
author: "Mehr Shafiq"
output: github_document
---

## Problem 1

*Setting up:*

```{r setup}
library(tidyverse)
```

*Create a data frame with the specified elements:*

```{r Data_frame}
prob1_df = tibble(
    sample = rnorm(10),
    samp_gt_0 = sample > 0,
    char_vec = c("a", "b", "c", "d", "e", "f", "g", "h", "i", "j"),
    factor_vec = factor(c("low", "low", "low", "mod", "mod", "mod", "mod", "high", "high", "high"))
  ) 
```

*Take the mean of each variable in my data frame:*

```{r mean_pull_var, eval = FALSE}
mean(pull(prob1_df, sample))
mean(pull(prob1_df, samp_gt_0))
mean(pull(prob1_df, char_vec))
mean(pull(prob1_df, factor_vec))
```
Means:

*   Sample: 0.4596784
*   Sample > 0: 0.7
*   Character vector: NA
*   Factor Vector: NA

Can only take the mean for numerical and logical variables, and not characters and factors. 

*Convert non-numeric variables to numeric variables:*

```{r, numeric_conversion, eval = FALSE}
as.numeric(pull(prob1_df, samp_gt_0))
as.numeric(pull(prob1_df, char_vec))
as.numeric(pull(prob1_df, factor_vec))
```
The logical variable gets converted to 0s and 1s. Characters can't be converted to numbers, and factors get converted to 1s, 2s, and 3s. We can calculate the mean for logical and factor variables. 

